Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-06-21 forecast/paper/paper.tex
Added author contributions.

% Please include corresponding author, author contribution and author
% declaration information 
\authorcontributions{Please provide details of author contributions here.}
\authordeclaration{Please declare any competing interests here.}
\correspondingauthor{\textsuperscript{1}To whom correspondence should be
  addressed. E-mail: daniel@stat.ubc.ca} 
\equalauthors{\textsuperscript{2}J.B., A.G., and A.J.H. contributed equally to 
  this work.}

>>>>

% Please include corresponding author, author contribution and author
% declaration information 
\authorcontributions{D.J.M., J.B., A.G., A.J.H., and R.J.T wrote the manuscript,
produced figures, and developed software necessary to perform the analyses. All
authors performed research and provided intellectual contributions. R.J.T
acquired funding.}
\authordeclaration{The authors have no competing interests to declare.}
\correspondingauthor{\textsuperscript{1}To whom correspondence should be
  addressed. E-mail: daniel@stat.ubc.ca} 
\equalauthors{\textsuperscript{2}J.B., A.G., and A.J.H. contributed equally to 
  this work.}
